Viscous Transport in Eroding Porous Media

### 2019-08-11 docs/transport/erosion_transport.tex
put some papers in the bib file for the introduction

\begin{itemize}
\item \cite{dar-mcc1998} show that if there is a region with high
porosity, this greatly affects the relationships between the porosity
and permeability.  Uses a Lattice-Boltzmann method.

\item Continuous Time Random Walks

@@

Having developed numerically accurate methods to compute the velocity
$\uu$ at points close to the bodies, we are able to compute the
trajectories of particles passing through an eroded body.  Since the
trajectories are computed with high-order methods in both space and
time,  we are able to simulate dynamics very close to the eroding bodies
(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.
Resolving the flow in these small velocity regions is essential to
accurately describe anomalous diffusion and
mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.

>>>>

\begin{itemize}
\item Porous aquifers are a good application of our work

\item \cite{dar-mcc1998} show that if there is a region with high
porosity, this greatly affects the relationships between the porosity
and permeability.  Uses a Lattice-Boltzmann method.

\item Continuous Time Random Walks~\cite{ber-cor-den-sch2006}

@@

Having developed numerically accurate methods to compute the velocity
$\uu$ at points close to the bodies, we are able to compute the
trajectories of particles passing through an eroded body.  Since the
trajectories are computed with high-order methods in both space and
time,  we are able to simulate dynamics very close to the eroding bodies
(see Figures~\ref{fig:Eroding20tracer} and~\ref{fig:Eroding100tort}.
Resolving the flow in these small velocity regions is essential to
accurately describe anomalous diffusion and
mixing~\cite{leb-den-dav-bol-car-dec-bou2011, den-leb-eng-bij2011}.
